\documentclass[12pt,preprint]{aastex}

%\usepackage{mparhack}
%\usepackage{numberparagraphs}
\newcommand{\numberparagraphs}{}
\newcommand{\nonumberparagraphs}{}

\newcommand{\doctype}{article\xspace}
\newcommand{\thesisonly}[1]{}
\newcommand{\notthesisonly}[1]{#1}
\renewcommand{\comment}[1]{}

\input{preamble}

\graphicspath{{figs-techreport/}}

\title{\an: \\
       Astrometric calibration of arbitrary astronomical images}
\author{Dustin~Lang\altaffilmark{1,2,3},
        David~W.~Hogg\altaffilmark{4,5},
        Keir~Mierle\altaffilmark{1,6},
        Michael~Blanton\altaffilmark{4},
        Sam~Roweis\altaffilmark{1,6}
}
\altaffiltext{1}{Department of Computer Science, University of Toronto,
                 6 King’s College Road, Toronto, Ontario, M5S~3G4 Canada}
\altaffiltext{2}{Princeton University Observatory, Princeton, NJ 08544, USA}
\altaffiltext{3}{to whom correspondence should be addressed: dstn@astro.princeton.edu}
\altaffiltext{4}{Center for Cosmology \& Particle Physics, Department of Physics,
                 New York University, 4 Washington Place, New York NY 10003, USA}
\altaffiltext{5}{Max-Planck-Institut f\"ur Astronomie,
                 K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{6}{Google Inc., Mountain View, CA}

\begin{abstract}
We have built a reliable and robust system that takes as input an
astronomical image, and returns as output the pointing, scale, and
orientation of that image (the astrometric calibration or WCS
information).  The system requires no first guess, and works with the
information in the image pixels alone; that is, the problem is a
generalization of the ``lost in space'' problem in which nothing---not
even the image scale---is known.  After robust source detection is
performed in the input image, asterisms (sets of four or five stars)
are geometrically hashed and compared to pre-indexed hashes to
generate hypotheses about the astrometric calibration.  A hypothesis
is only accepted as true if it passes a Bayesian decision theory test
against a null hypothesis.  With indices built from the USNO-B Catalog
and designed for uniformity of coverage and redundancy, the success
rate is $>99.9~\percent$ for contemporary near-ultraviolet and visual
imaging survey data, with no false positives.  The failure rate is
consistent with the incompleteness of the USNO-B Catalog; augmentation
with indices built from the 2MASS Catalog brings the completeness to
$100~\percent$ with no false positives.  We are using this system to
generate consistent and standards-compliant meta-data for digital and
digitized imaging from plate repositories, automated observatories,
individual scientific investigators, and hobbyists.  This is the first
step in a program of making it possible to trust calibration meta-data
for astronomical data of arbitrary provenance.
\end{abstract}

\keywords{
astrometry
---
catalogs
---
instrumentation: miscellaneous
---
methods: data analysis
---
methods: statistical
---
techniques: image processing
}

\begin{document}
\maketitle

\input{tech-report}

{\small
\bibliographystyle{plain}
\bibliography{tech-report-wrapper}
}

\end{document}

