\documentclass[letterpaper]{ut-thesis}
% twoside
%\documentclass[draft,12pt]{ut-thesis}


\usepackage{mparhack}
\usepackage{numberparagraphs}
\usepackage{svn}
% don't indent footnotes.
\usepackage[hang,flushmargin]{footmisc}

%\newcommand{\numberparagraphs}{}
%\newcommand{\nonumberparagraphs}{}

%\SVN $Revision: 13655 $
%\SVN $Date: 2009-11-17 13:39:31 -0500 (Tue, 17 Nov 2009) $

% Small margins
\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\-\oldmarginpar{\footnotesize #1}}
% Put the margin notes on the left-hand margin.
\reversemarginpar

\newcommand{\doctype}{chapter\xspace}
\newcommand{\thesisonly}[1]{#1}
\newcommand{\notthesisonly}[1]{}

\input{aastex_defines}
\input{preamble}

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{2}

\newcommand{\mytitle}{\an: Automatic recognition and calibration of astronomical images}
\newcommand{\myauthor}{Dustin Lang}

\degree{Doctor of Philosophy}
\department{Computer Science}
\gradyear{2009}
\author{\myauthor}
\title{\mytitle}
%\titlepagefootnote{\noindent This is Subversion revision \SVNRevision\ in the \an repository, dated \SVNDate\ at \SVNTime.}

\hypersetup{
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfsubject={Astrometry.net.},%  This is SVN revision \SVNRevision, dated \SVNDate\ at \SVNTime.},
  pdfkeywords={Astrometry, Astrometry.net, Geometric hashing, Kd-tree, kdtree},
  letterpaper=true,
  setpagesize=true,
}

\sloppy

\begin{document}

\begin{preliminary}
\maketitle

%% (At most 150 words for M.Sc. or 350 words for Ph.D.)
\begin{abstract}
We present \an, a system for automatically recognizing and
astrometrically calibrating astronomical images, using the information
in the image pixels alone.  The system is based on the \emph{geometric
  hashing} approach in computer vision: We use the geometric
relationships between low-level features (stars and galaxies), which
are relatively indistinctive, to create geometric features that are
distinctive enough that we can recognize images that cover less than
one-millionth of the area of the sky.  The geometric features are used
to generate rapidly hypotheses about the location---the pointing,
scale, and rotation---of an image on the sky.  Each hypothesis is then
evaluated in a Bayesian decision theory framework in order to ensure
that most correct hypotheses are accepted while false hypotheses are
almost never accepted.  The feature-matching process is
accelerated by using a new fast and space-efficient \kdtree
implementation.  The \an system is available via a web interface, and
the software is released under an open-source license.  It is being
used by hundreds of individual astronomers and several large-scale
projects, so we have at least partially achieved our goal of helping
``to organize, annotate and make searchable all the world's
astronomical information.''
\end{abstract}

\begin{acknowledgements}

First, I want to thank Sam Roweis for accepting me as his student, for
handing me the nascent \an project which has been so fun to work on,
for providing help, support, and encouragement throughout, and, most
importantly, for his warm friendship.


I owe huge thanks to David Hogg, for serving as my semi-official
co-supervisor, mentor, and guide to the world of astronomy.  It is
hard to imagine what my life would be like if I hadn't met him: no
Delion-fuelled hack sessions in New York, no lovely summers in
Heidelberg, and I almost certainly would not have made the jump into
astronomy.  He has shown me a great deal about how to be a good
scientist and how to love my job and love my family at the same time.
It has been a great privilege working with him.


I have been fortunate to work with a number of great people on the \an
team, in particular Keir Mierle, who taught me many things about the
practice of software development, and Christopher Stumm, who has done
excellent work in bringing \an to the amateur astronomy community.
%; and Jon Barron, who has a knack for getting papers published.
I must also thank the army of alpha-testers who have provided a lot of
bug reports, great ideas for improving the system, and some very
encouraging feedback.


%I thank my office-mates for putting up with my overflowing desk full
%of junk, and for providing such a great environment in which to work.
%I thank Relu for keeping everything running, and for amusing us with
%his lack-of-political-correctness antics.  I thank the lunch crew for
%providing some genuine social interaction, and more than a few
%hare-brained schemes and whit


It is a pleasure to thank Iain Murray for many helpful ideas and
insights; for listening politely while I rambled about some
half-understood problem I was working on; and for being so amusingly
English.


I thank Sven Dickinson and Rich Zemel for serving on my advisory
committee.  They provided excellent guidance, advice, and suggestions
for improving this thesis.  I thank Doug Finkbeiner for taking the
time to read my thesis and provide thoughtful comments, and for
travelling to Toronto to serve as my external examiner.


I thank my mom and my brother, Gerda and Devon Lang, who are two
fantastic people who have always been there for me.


I give huge thanks to my lovely wife Micheline.  A PhD is a
team effort, and she is the foundation of Team Lang.  She provided a
huge amount of love and encouragement, proof-read thesis drafts,
forced me to practice my talks and listened patiently while I did, and
kept our household running while I was embroiled in writing.  I
couldn't have done it without her.  There are exciting times ahead and
I'm so very happy to have her at my side.

Finally, I thank my baby son Julian
for having brought so much joy into our lives, and
for sleeping soundly while I write these words.

\end{acknowledgements}

\tableofcontents

%\listoftables
%\listoffigures

\end{preliminary}

\numberparagraphs

\chapter{Introduction}
\graphicspath{{figs-review/}}
\include{review}

\chapter[\antitle: recognizing astronomical images]
		{\an: recognition of arbitrary astronomical images%
		  \footnote{This chapter was originally prepared as a manuscript
			by me, David~W.~Hogg, Keir~Mierle, Michael~Blanton, and
			Sam~Roweis.}}
\label{chap:techreport}
\graphicspath{{figs-techreport/}}
\include{tech-report}

\chapter[Verifying an astrometric alignment]
        {Verifying a proposed alignment between astronomical images}
\label{chap:verify}
\graphicspath{{figs-verify/}}
\input{verify}

\chapter[Efficient implementation of \kdtreestitle]
		{Efficient implementation of the \kdtreetitle data structure%
        \footnote{This chapter was originally prepared as a manuscript
        by me, Keir Mierle, and Aeron Buchanan.}}
\label{chap:kdtree}
\graphicspath{{figs-kdtree/}}
\include{kdtree}

\chapter{Conclusion}
\label{chap:conclusion}
\include{conclusion}

\nonumberparagraphs

\addcontentsline{toc}{chapter}{Bibliography}

%% (change according to your preference)
\bibliographystyle{plain}
\bibliography{thesis}

\end{document}
